Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-24 hpmoon-asoco.tex
Minor changes

This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
Econom{\'ia}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.

>>>>

This work has been partially funded by project SPIP2017-02116 (Spanish ``Direcci\'on General de Tr\'afico''), and projects, TIN2015-67020-P, DeepBio TIN2017-85727-C4-2-P  and TEC2015-68752 (Spanish ``Ministerio de
Econom{\'i}a y Competitividad'') and PGC2018-098813-B-C31 (Spanish ``Ministerio de Ciencia, Innovación y Universidades''), and by European Regional Development Funds (ERDF).
We would like to express our gratitude to the editorial team and the reviewers, whose valuable comments on this paper have significantly improved its quality.
